Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-13 paper.qmd
Updated Figure 8

error_plot_two_curvy <-
  plot_mse(error_two_curvy) +
  scale_x_continuous(breaks =
    sort(unique(error_two_curvy$a1))[
      seq(1, length(
        unique(error_two_curvy$a1)), 
        by = 5)]) +
  scale_color_manual(
    values=c('#e41a1c','#ff7f00','#4daf4a', 
             "#a65628",'#636363', '#984ea3')) +
  scale_y_log10() + 
  theme(aspect.ratio = 1.5)
```

>>>>

error_plot_two_curvy <-
  plot_mse(error_two_curvy) +
  scale_x_continuous(breaks =
    sort(unique(error_two_curvy$a1))[
      seq(1, length(
        unique(error_two_curvy$a1)), 
        by = 5)]) +
  scale_color_manual(
    values=c('#e41a1c','#ff7f00','#4daf4a', 
             "#a65628",'#636363', '#984ea3')) +
  theme(aspect.ratio = 1.5)
```
